\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-01-23 papers/jss/article.Rnw
Minor grammar improvements suggested by my office mate Arif Merchant. Mostly involving that/which.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@831 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

While traditional IDLs have at times been criticized for code bloat and
complexity, Protocol Buffers are based on a simple list and records
model that is flexible and simple to use.  The schema for structured
protocol buffer data is defined in \texttt{.proto} files which may
contain one or more message types.  Each message type has one or more
fields.  A field is specified with a unique number, a name, a value
type, and a field rule specifying whether the field is optional,
required, or repeated.  The supported value types are numbers,
enumerations, booleans, strings, raw bytes, or other nested message
types.  The \texttt{.proto} file syntax for defining the structure of protocol
buffer data is described comprehensively on Google Code\footnote{See 
\url{http://code.google.com/apis/protocolbuffers/docs/proto.html}.}.
Table~\ref{tab:proto} shows an example \texttt{.proto} file which
defines the \texttt{tutorial.Person} type.  The \proglang{R} code in the right
column shows an example of creating a new message of this type and
populating its fields.

@@

However, as opposed to \proglang{R} lists, no partial matching is performed
and the name must be given entirely.
The \verb|[[| operator can also be used to query and set fields
of a messages, supplying either their name or their tag number :

>>>>

While traditional IDLs have at times been criticized for code bloat and
complexity, Protocol Buffers are based on a simple list and records
model that is flexible and easy to use.  The schema for structured
protocol buffer data is defined in \texttt{.proto} files, which may
contain one or more message types.  Each message type has one or more
fields.  A field is specified with a unique number, a name, a value
type, and a field rule specifying whether the field is optional,
required, or repeated.  The supported value types are numbers,
enumerations, booleans, strings, raw bytes, or other nested message
types.  The \texttt{.proto} file syntax for defining the structure of protocol
buffer data is described comprehensively on Google Code\footnote{See 
\url{http://code.google.com/apis/protocolbuffers/docs/proto.html}.}.
Table~\ref{tab:proto} shows an example \texttt{.proto} file that
defines the \texttt{tutorial.Person} type.  The \proglang{R} code in the right
column shows an example of creating a new message of this type and
populating its fields.

@@

As opposed to \proglang{R} lists, no partial matching is performed
and the name must be given entirely.
The \verb|[[| operator can also be used to query and set fields
of a messages, supplying either their name or their tag number :
